Integer Programming Formulations for the Shared Multicast Tree Problem

### 2018-12-27 smt/sec4-milp.tex
MI: Remarks from minor revision incorporated - mostly typos and grammar.

\begin{lemma} \label{lem:x0valid}
If $(X,y)$ satisfies (\ref{con:dd:arrowFromDest})--(\ref{con:dd:vardim}), then $G_y$ has a tree spanning $D$ as one of its connected components.
Conversely, for any tree $T\subseteq G$ spanning $D$, there exists a pair $(X,y)$ satisfying (\ref{con:dd:arrowFromDest})--(\ref{con:dd:vardim}) such that $T$
is a connected component of $G_y$.
\end{lemma}
\begin{proof}
By (\ref{con:dd:startInSource}) and (\ref{con:dd:arrowFromDest})--(\ref{con:dd:arrowFromNonDestB}),
the in-degree of $s\in D$ is 0 in $G_{X^s}$, whereas it is at most one at all other nodes.
Hence, the connected components of $G_{X^s}$ are directed cycles, arborescences, and isolated nodes,
and one of the components is an arborescence rooted at $s$.
Constraints (\ref{con:dd:oneDir}) imply that $G_y$ consists of undirected versions of the same components,
showing that no cycle in $G_y$ contains destination nodes.
Let $t\in D$, and let $P$
be the maximal path in $G_{X^s}$ that terminates in $t$.
Existence and uniqueness of this path is assured since $t$ belongs to an acyclic connected component.
According to (\ref{con:dd:arrowFromNonDestA}), each non-destination in $P$ has an entering arc in $P$,
while (\ref{con:dd:arrowFromDest}) ensures that the same is true for every destination node, except $s$.
It follows that the first node of $P$ is $s$.
Thus, destinations $s$ and $t$ belong to a joint, acyclic connected component of $G_y$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                     % 
%             MODEL X1                %
%           (3 idx vars)              %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{subequations}[resume]\label{eq:smt-x2}
\begin{align}
\label{objective:mf} \makebox[0pt][l]{$\displaystyle{} \min \sum\limits_{(i,j) \in A} p_{ij} \sum\limits_{s \in D} \pi^s_{ij} $}\\
\notag\text{s.t.}\\
\notag(\ref{con:dd:arrowFromDest}) &- (\ref{con:dd:vardim})\\
\label{con:dd:yvar} X^s_{ij} & \leq \sum_{k\in W_{ij}}\pi^s_{ik} & s\in D, (i,j)\in A,\\
\label{con:dd:vardimy} \pi & \in \{0,1\}^{A\times D}.
\end{align}~
\end{subequations}

@@

\begin{prop}
\label{prop:x1valid}
If $(X,y,\pi)$ is an optimal solution to $\mathcal{X}_1$, then $G_y$ consists of isolated non-destination nodes and a tree that
solves Problem \ref{def:problem}.
\end{prop}
\begin{proof}
Follows directly from $p\geq 0$ and Lemma \ref{lem:x0valid}.
\qed
\end{proof}

@@

Adding the following valid inequalities to $\mathcal{X}_1$ gives another SMT-model, denoted $\mathcal{X}_2$:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                     % 
%             MODEL X2                %
%      (3 idx vars + VIs )            %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{subequations}[resume]
\begin{align}
\label{con:dd:extraCon} \sum\limits_{j\in V_{i}}X^s_{ji} & \leq \sum\limits_{j\in V_{i}}X^s_{ij}  & 	i\in V\setminus D, s\in D,\\
\label{con:vi:Y1} \sum\limits_{j\in V_s}  \pi^{s}_{sj} & =1 & s\in D,\\
\label{con:vi:sumYImpSumX} \sum\limits_{j\in V_i\setminus\{s\} }\pi^{s}_{ij} & = \sum\limits_{j\in V_i}  X^{s}_{ji} & i\in V\setminus D, s\in D.
\end{align}
\end{subequations}
Constraints (\ref{con:dd:extraCon}) ensure that the number of arcs leaving a non-destination in $T^s$ is no less than the number of entering arcs.
Their effect is to disallow non-destination leaves.
Equations (\ref{con:vi:Y1}) say that in arborescence $T^s$, exactly one arc $(s,j)$ leaving the root $s$ is declared to be largest.
Validity of the constraints follows immediately because the root has at least one leaving arc.
As constraints (\ref{con:vi:sumYImpSumX}) state, if an arc enters non-destination node $i$ in $T^s$, then $i$ also has at least one out-going arc,
exactly one of which is the most expensive.
The root $s$ is excluded from the summation set on the left of (\ref{con:vi:sumYImpSumX}) since no arcs in $T^s$ enter $s$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                     %
%         Proposition  		      %
% (F1 models an arborescence)         %
%                                     %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{lemma}
\label{lem:modelcorrect}
Assume $(F,g)$ satisfies (\ref{con:pf1:xfrel})--(\ref{con:pf1:dim}).
Then some connected component $T^0\subseteq G_{g}$ is an $s_0$-rooted arborescence spanning $D$,
and some connected component of $G_{F^s}\subseteq T^0$ is a path from $s_0$ to $s\in D_0$.
Conversely, for any $s_0$-rooted arborescence $T^0$ spanning $D$, there exists a pair $(F,g)$ satisfying (\ref{con:pf1:xfrel})--(\ref{con:pf1:dim}) such that $T^0$
is a connected component of $G_g$.
\end{lemma}

To model the objective function of SMT, the following result is useful:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                     %
%         Proposition  		      %
%   (transformation X_{ij}^s)         %
%                                     %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{prop}\label{prop:transx}
Assume $(F,g)$ satisfies (\ref{con:pf1:xfrel})--(\ref{con:pf1:dim}),
and let $T^s=(V^s,A^s)$ be the arborescence obtained by redirecting the arcs in $T^0$ such that they point away from $s\in D_0$. Then
$$
g_{ij} - F^s_{ij}+F^s_{ji} = 
	\begin{cases}
		1, ~\text{if $(i,j)\in A^s$}, \\
		0, ~\text{otherwise.}
	\end{cases}
$$
\end{prop}
%
\begin{proof}
Because $T^0$ is acyclic, it follows from the capacity constraints (\ref{con:pf1:xfrel}) that $g_{ij}+F^s_{ji}\leq 1$.
The same constraints also imply $g_{ij} - F^s_{ij}\geq 0$.
Hence, $g_{ij} - F^s_{ij}+F^s_{ji}\in\{0,1\}$.

Arborescence $T^s$ contains arc $(i,j)$ iff $(i,j)$ is in $A^0$ but not on a path to $s$, or its reverse arc $(j,i)$ is on such a path.
By Lemma \ref{lem:modelcorrect}, this disjunction is equivalent to $g_{ij}-F_{ij}^s=1$ or $F_{ji}=1$.
The result then follows since the two conditions are mutually exclusive.
\qed
\end{proof}

@@

Recall from Section \ref{sec:x1} that $\pi_{ij}^s$ determines whether $(i,j)$ is the most expensive arc leaving node $i$ in arborescence $T^s$.
Taking advantage of Prop.\ \ref{prop:transx}, we can thus formulate Problem \ref{def:problem} in terms of variables $F$, $g$, and $\pi$,
resulting in model $\mathcal{F}_1$:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                     % 
%             MODEL F1                %
%        (3 idx vars)                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{subequations}[resume]
\begin{align}
\notag\min & \sum\limits_{(i,j) \in A} p_{ij} \sum\limits_{s \in D} \pi^s_{ij}\\ 
\notag\text{s.t.} && \\
\notag(\ref{con:pf1:xfrel}) - (\ref{con:pf1:dim})\\
\label{con:pf1:yvar} g_{ij} - F^s_{ij}+F^s_{ji} & \leq \sum_{k\in W_{ij}}\pi^s_{ik}  & s\in D_0, (i,j)\in A,\\
\label{con:pf1:yvar0} g_{ij} & \leq \sum_{k\in W_{ij}}\pi^0_{ik}   &  (i,j)\in A,\\
\label{con:pf1:dimy} \pi&\in \{0,1\}^{A\times D}.
\end{align}~
\end{subequations}

@@

According to Prop.\ \ref{prop:transx}, if $i\in V\setminus D$ and $g_{ji} - F^s_{ji}+F^s_{ij}=1$ for some $j\in V_i$ and $s\in D_0$,
then $i$ is a Steiner node used to establish connection between $s$ and some other destination.
Since $i$ also has a leaving arc in $T^s$, we have $\pi_{ik}^s=1$ for some $k\neq i,s$.
This proves validity of the constraint $\sum_{j\in V_i}\left(g_{ji} - F^s_{ji}+F^s_{ij}\right)=\sum_{j\in V_i\setminus\{s\}}\pi_{ij}^s$
Application of flow conservation (\ref{con:pf1:flow}) yields the valid constraints
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                     %
%             MODEL F2                %
%                                     %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{subequations}[resume]
\begin{flalign}
\label{con:vi:sumYImpSumXTrans} \sum\limits_{j\in V_i\setminus\{s\}}\pi^{s}_{ij} & = \sum\limits_{j\in V_i}  g_{ji}  \quad\quad   i\in V\setminus D, s\in D. 
\end{flalign}
\end{subequations}

\noindent
Finally, constraints (\ref{con:vi:Y1}) are valid,
completing formulation $\mathcal{F}_2$ as model $\mathcal{F}_1$ extended by (\ref{con:pf1:flowX})--(\ref{con:vi:sumYImpSumXTrans}) and (\ref{con:vi:Y1}).
%
\begin{remark} \label{rem:f2}
With $s_0$ equal to the destination node in position (47, 65), the instance given in Remark \ref{rem:x2} also proves independence of the three sets
(\ref{con:vi:Y1}), (\ref{con:vi:sumYImpSumXTrans})--(\ref{con:pf1:flowX}) of valid inequalities.
\end{remark}

>>>>

\begin{lemma} \label{lem:x0valid}
If $(X,y)$ satisfies (\ref{con:dd:arrowFromDest})--(\ref{con:dd:vardim}), then $G_y$ has a tree spanning $D$ as one of its connected components.
Conversely, for any tree $T\subseteq G$ spanning $D$, there exists a pair $(X,y)$ satisfying (\ref{con:dd:arrowFromDest})--(\ref{con:dd:vardim}) such that $T$
is a connected component of $G_y$.
\end{lemma}
\begin{proof}
By (\ref{con:dd:startInSource}) and (\ref{con:dd:arrowFromDest})--(\ref{con:dd:arrowFromNonDestB}),
the in-degree of $s\in D$ is 0 in $G_{X^s}$, whereas it is at most one at all other nodes.
Hence, the connected components of $G_{X^s}$ are directed cycles, arborescences, and isolated nodes,
and one of the components is an arborescence rooted at $s$.
Constraints (\ref{con:dd:oneDir}) imply that $G_y$ consists of undirected versions of the same components,
showing that no cycle in $G_y$ contains destination nodes.
Let $t\in D$, and let $P$
be the maximal path in $G_{X^s}$ that terminates in $t$.
Existence and uniqueness of this path are assured since $t$ belongs to an acyclic connected component.
According to (\ref{con:dd:arrowFromNonDestA}), each non-destination in $P$ has an entering arc in $P$,
while constraints (\ref{con:dd:arrowFromDest}) ensure that the same is true for every destination node, except $s$.
It follows that the first node of $P$ is $s$.
Thus, destinations $s$ and $t$ belong to a joint, acyclic connected component of $G_y$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                     % 
%             MODEL X1                %
%           (3 idx vars)              %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{subequations}[resume]\label{eq:smt-x2}
\begin{align}
\label{objective:mf} \makebox[0pt][l]{$\displaystyle{} \min \sum\limits_{(i,j) \in A} p_{ij} \sum\limits_{s \in D} \pi^s_{ij}, $}\\
\notag\text{s.t.}\\
\notag(\ref{con:dd:arrowFromDest}) &- (\ref{con:dd:vardim}),\\
\label{con:dd:yvar} X^s_{ij} & \leq \sum_{k\in W_{ij}}\pi^s_{ik} & s\in D, (i,j)\in A,\\
\label{con:dd:vardimy} \pi & \in \{0,1\}^{A\times D}.
\end{align}~
\end{subequations}

@@

\begin{prop}
\label{prop:x1valid}
If $(X,y,\pi)$ is an optimal solution to $\mathcal{X}_1$, then $G_y$ consists of isolated non-destination nodes and a tree that
solves Problem \ref{def:problem}.
\end{prop}
\begin{proof}
Follows directly from $p>0$ and Lemma \ref{lem:x0valid}.
\qed
\end{proof}

@@

Adding the following valid inequalities to $\mathcal{X}_1$ gives another SMT-model, denoted $\mathcal{X}_2$:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                     % 
%             MODEL X2                %
%      (3 idx vars + VIs )            %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{subequations}[resume]
\begin{align}
\label{con:dd:extraCon} \sum\limits_{j\in V_{i}}X^s_{ji} & \leq \sum\limits_{j\in V_{i}}X^s_{ij}  & 	i\in V\setminus D, s\in D,\\
\label{con:vi:Y1} \sum\limits_{j\in V_s}  \pi^{s}_{sj} & =1 & s\in D,\\
\label{con:vi:sumYImpSumX} \sum\limits_{j\in V_i\setminus\{s\} }\pi^{s}_{ij} & = \sum\limits_{j\in V_i}  X^{s}_{ji} & i\in V\setminus D, s\in D.
\end{align}
\end{subequations}
Constraints (\ref{con:dd:extraCon}) ensure that the number of arcs leaving a non-destination in $T^s$ is no less than the number of entering arcs.
Their effect is to disallow non-destination leaves.
Equations (\ref{con:vi:Y1}) say that in arborescence $T^s$, exactly one arc $(s,j)$ leaving the root $s$ is declared to be the largest.
Validity of the constraints follows immediately because the root has at least one leaving arc.
As constraints (\ref{con:vi:sumYImpSumX}) state, if an arc enters non-destination node $i$ in $T^s$, then $i$ also has at least one out-going arc,
exactly one of which is the most expensive.
The root $s$ is excluded from the summation set on the left of (\ref{con:vi:sumYImpSumX}) since no arcs in $T^s$ enter $s$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                     %
%         Proposition  		      %
% (F1 models an arborescence)         %
%                                     %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{lemma}
\label{lem:modelcorrect}
Assume $(F,g)$ satisfies (\ref{con:pf1:xfrel})--(\ref{con:pf1:dim}).
Then, some connected component $T^0\subseteq G_{g}$ is an $s_0$-rooted arborescence spanning $D$,
and some connected component of $G_{F^s}\subseteq T^0$ is a path from $s_0$ to $s\in D_0$.
Conversely, for any $s_0$-rooted arborescence $T^0$ spanning $D$, there exists a pair $(F,g)$ satisfying (\ref{con:pf1:xfrel})--(\ref{con:pf1:dim}) such that $T^0$
is a connected component of $G_g$.
\end{lemma}

To model the objective function of SMT, the following result is useful:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                     %
%         Proposition  		      %
%   (transformation X_{ij}^s)         %
%                                     %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{prop}\label{prop:transx}
Assume $(F,g)$ satisfies (\ref{con:pf1:xfrel})--(\ref{con:pf1:dim}),
and let $T^s=(V^s,A^s)$ be the arborescence obtained by redirecting the arcs in $T^0$ such that they point away from $s\in D_0$. 
Then,
$$
g_{ij} - F^s_{ij}+F^s_{ji} = 
	\begin{cases}
		1, ~\text{if $(i,j)\in A^s$}, \\
		0, ~\text{otherwise.}
	\end{cases}
$$
\end{prop}
%
\begin{proof}
Because $T^0$ is acyclic, $g_{ij}+g_{ji}\leq 1$, and it follows from the capacity constraints (\ref{con:pf1:xfrel}) that $g_{ij}+F^s_{ji}\leq 1$.
The same constraints also imply $g_{ij} - F^s_{ij}\geq 0$.
Hence, $g_{ij} - F^s_{ij}+F^s_{ji}\in\{0,1\}$.

Arborescence $T^s$ contains arc $(i,j)$ iff $(i,j)$ is in $A^0$ but not on a path to $s$, or its reverse arc $(j,i)$ is on such a path.
By Lemma \ref{lem:modelcorrect}, this disjunction is equivalent to $g_{ij}-F_{ij}^s=1$ or $F_{ji}^s=1$.
The result then follows since the two conditions are mutually exclusive.
\qed
\end{proof}

@@

Recall from Section \ref{sec:x1} that $\pi_{ij}^s$ determines whether $(i,j)$ is the most expensive arc leaving node $i$ in arborescence $T^s$.
Taking advantage of Prop.\ \ref{prop:transx}, we can thus formulate Problem \ref{def:problem} in terms of variables $F$, $g$, and $\pi$,
resulting in model $\mathcal{F}_1$:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                     % 
%             MODEL F1                %
%        (3 idx vars)                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{subequations}[resume]
\begin{align}
\notag\min & \sum\limits_{(i,j) \in A} p_{ij} \sum\limits_{s \in D} \pi^s_{ij},\\ 
\notag\text{s.t.} && \\
\notag(\ref{con:pf1:xfrel}) - (\ref{con:pf1:dim}),\\
\label{con:pf1:yvar} g_{ij} - F^s_{ij}+F^s_{ji} & \leq \sum_{k\in W_{ij}}\pi^s_{ik}  & s\in D_0, (i,j)\in A,\\
\label{con:pf1:yvar0} g_{ij} & \leq \sum_{k\in W_{ij}}\pi^0_{ik}   &  (i,j)\in A,\\
\label{con:pf1:dimy} \pi&\in \{0,1\}^{A\times D}.
\end{align}~
\end{subequations}

@@

According to Prop.\ \ref{prop:transx}, if $i\in V\setminus D$ and $g_{ji} - F^s_{ji}+F^s_{ij}=1$ for some $j\in V_i$ and $s\in D_0$,
then $i$ is a Steiner node used to establish connection between $s$ and some other destination.
Since $i$ also has a leaving arc in $T^s$, we have $\pi_{ik}^s=1$ for some $k\neq i,s$.
This proves validity of the constraint $\sum_{j\in V_i}\left(g_{ji} - F^s_{ji}+F^s_{ij}\right)=\sum_{j\in V_i\setminus\{s\}}\pi_{ij}^s$.
Application of flow conservation (\ref{con:pf1:flow}) yields the valid constraints
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                     %
%             MODEL F2                %
%                                     %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{subequations}[resume]
\begin{flalign}
\label{con:vi:sumYImpSumXTrans} \sum\limits_{j\in V_i\setminus\{s\}}\pi^{s}_{ij} & = \sum\limits_{j\in V_i}  g_{ji}  \quad\quad   i\in V\setminus D, s\in D. 
\end{flalign}
\end{subequations}

\noindent
Finally, constraints (\ref{con:vi:Y1}) are valid,
completing formulation $\mathcal{F}_2$ as model $\mathcal{F}_1$ extended by (\ref{con:pf1:flowX})--(\ref{con:vi:sumYImpSumXTrans}) and (\ref{con:vi:Y1}).
%
\begin{remark} \label{rem:f2}
With $s_0$ equal to the destination node in position (47, 65), the instance given in Remark \ref{rem:x2} also proves independence of the three sets
(\ref{con:vi:Y1}), (\ref{con:pf1:flowX})--(\ref{con:vi:sumYImpSumXTrans}) of valid inequalities.
\end{remark}

### 2018-12-27 smt/sec5-relations.tex
MI: Remarks from minor revision incorporated - mostly typos and grammar.

\begin{lemma} \label{lem:lpf1gijgji}
If $(F,g,\pi)$ is feasible in $\text{LP}(\mathcal{F}_1)$ with (\ref{eq:lemlpf1a})--(\ref{eq:lemlpf1b}) satisfied, then
\begin{equation}
\begin{aligned}
 & g_{ij}+g_{ji} \leq 1 & \{i,j\}\in E. \label{eq:lemlpf1c}
\end{aligned}
\end{equation}
\end{lemma}
\begin{proof}
Assume $g_{ij}+g_{ji}>1$ for some $\{i,j\}\in E$.
Because $g_{i0}=0$, this implies $i\neq s_0\neq j$.
By (\ref{eq:lemlpf1b}), there exist $s,t\in D_0$ such that $F_{ij}^s+F_{ji}^t>1$.
According to (\ref{eq:lemlpf1a}), $F_{ij}^s>1-F_{ji}^t\geq 0$ shows that $F_{ji}^s=0$.
Flow conservation at node $i$ thus implies $1<F_{ij}^s+F_{ji}^t\leq\sum_{k\in V_i\setminus\{j\}}F_{ki}^s+F_{ji}^t
\leq\sum_{k\in V_i\setminus\{j\}}g_{ki}+g_{ji}$, contradicting Lemma \ref{lem:lpf1feas}.\qed
\end{proof}

@@

For $j\in D_0$ (for $j=s_0$), (\ref{eq:lemlpf2b}) follows directly from (\ref{con:pf1:fitt=xit}) (from (\ref{con:pf1:xi0=0})).
Consider an $i\in D$ and $j\in V_i$ such that $g_{ij}>F_{ij}^*$.
Reducing $g_{ij}$ to $F_{ij}^*$, while keeping all other variables unchanged, preserves feasibility and the objective function value.
Thus, $(F,g)$ is henceforth assumed to satisfy (\ref{eq:lemlpf2b}).

@@

Let $(j_1,\ldots,j_p)$ be a path with $p\geq 1$ nodes in $H[F,g]$, such that $j_p$ has no out-neighbors in $H[F,g]$.
Node $j_p$ exists since the digraph is acyclic.
Define the maximum capacity reduction as
\[ \sigma^*=\min\left\{\sigma_{j_0j_1}(F,g),\min\left\{g_{j_l,j_{l+1}}-F^*_{j_l,j_{l+1}}: l=1,\ldots,p-1\right\}\right\}>0.\]
Let $\tilde{g}_{j_lj_{l+1}}=g_{j_lj_{l+1}}-\sigma^*$ for $l=0,1,\ldots,p-1$, and let $\tilde{g}_{ij}=g_{ij}$ for all other arcs $(i,j)\in A$.
Then $(F,\tilde{g},\pi)$ is feasible since, in comparison to $(F,g,\pi)$,  the left hand side of inequality (\ref{con:pf1:flowX}) is
increased by no more than the current slack at node $i=j_0$, reduced at node $i=j_p$, and unchanged at all other nodes $i\in V\setminus D$.
For all arcs $(i,j)$ between non-destination nodes, $\sigma_{ij}(F,\tilde{g})\leq\sigma_{ij}(F,g)$, except from arcs for which $i=j_p$.
But since $(j_p,j)\not\in A[F,g]$, $\sigma_{j_pj}(F,g)>0$.
% and the capacity reduction introduces no new violations of (\ref{eq:lemlpf2a})--(\ref{eq:lemlpf2c}).
It is finally observed that $\sigma_{j_0j_1}(F,\tilde{g})=0$ if $\sigma^*=\sigma_{j_0j_1}(F,g)$,
and that $\left(j_l,j_{l+1}\right)\in A[F,g]\setminus A[F,\tilde{g}]$ if $\sigma^*=g_{j_l,j_{l+1}}-F^*_{j_l,j_{l+1}}$ for some $l=1,\ldots,p-1$.
\qed\end{proof}

@@

Assume first that $g_{ij}=F_{ij}^*$.
Then there exists a destination node $t\in D_0\setminus\{i\}$ such that $F_{ij}^t=g_{ij}$.
Because (\ref{eq:lemlpf1a}) gives $F_{ji}^t=0$, flow conservation (\ref{con:pf1:flow}) at node $i$ implies 
$g_{ij}=F_{ij}^t\leq \sum_{k\in V_i\setminus\{j\}}F_{ki}^t\leq \sum_{k\in V_i\setminus\{j\}}g_{ki}$.

@@

The proof that $(X,y,\pi)$ satisfies constraints (\ref{con:dd:arrowFromDest})--(\ref{con:dd:arrowFromNonDestB}), (\ref{con:dd:oneDir})--(\ref{con:dd:startInSource}),
and (\ref{con:dd:yvar}),
follows the proof of Prop.\ \ref{prop:f1strx1}.
To prove (\ref{con:dd:arrowFromNonDestA}), let $i\in V\setminus D$, $j\in V_i$, and $s\in D$.
Then transformations (\ref{eq:trangX0})--(\ref{eq:trangX}) yield
$X_{ij}^s - \sum_{k\in V_{i}\setminus \{j\}}X_{ki}^s
= g_{ij} - \sum_{k\in V_{i}\setminus \{j\}}g_{ki}$, and (\ref{con:dd:arrowFromNonDestA}) follows from (\ref{eq:lemlpf2d}) in Lemma \ref{lem:lpf2gijgji}.
Because Lemma \ref{lem:lpf2gijgji} also states that $g_{ij}+g_{ji}\leq 1$, we further have that $X_{ij}^s\in[0,1]$ and $y_{ij}\in[0,1]$.

>>>>

\begin{lemma} \label{lem:lpf1gijgji}
If $(F,g,\pi)$ is feasible in $\text{LP}(\mathcal{F}_1)$ with (\ref{eq:lemlpf1a})--(\ref{eq:lemlpf1b}) satisfied, then
\begin{equation}
\begin{aligned}
 & g_{ij}+g_{ji} \leq 1 & \text{ for all } \{i,j\}\in E. \label{eq:lemlpf1c}
\end{aligned}
\end{equation}
\end{lemma}
\begin{proof}
Assume $g_{ij}+g_{ji}>1$ for some $\{i,j\}\in E$.
Because $g_{i0}=0$, this implies $i\neq s_0\neq j$.
By (\ref{eq:lemlpf1b}), there exist $s,t\in D_0$ such that $F_{ij}^s+F_{ji}^t>1$.
According to (\ref{eq:lemlpf1a}), $F_{ij}^s>1-F_{ji}^t\geq 0$ shows that $F_{ji}^s=0$.
Flow conservation at node $i$ thus implies $1<F_{ij}^s+F_{ji}^t\leq\sum_{k\in V_i\setminus\{j\}}F_{ki}^s+F_{ji}^t
\leq\sum_{k\in V_i\setminus\{j\}}g_{ki}+g_{ji}$, contradicting Lemma \ref{lem:lpf1feas}.\qed
\end{proof}

@@

For $j\in D_0$ (for $j=s_0$), (\ref{eq:lemlpf2b}) follows directly from (\ref{con:pf1:fitt=xit}) (from (\ref{con:pf1:xi0=0})).
Consider an $i\in D$ and $j\in V_i\setminus D$ such that $g_{ij}>F_{ij}^*$.
Reducing $g_{ij}$ to $F_{ij}^*$, while keeping all other variables unchanged, preserves feasibility and the objective function value.
Thus, $(F,g)$ is henceforth assumed to satisfy (\ref{eq:lemlpf2b}).

@@

Let $(j_1,\ldots,j_p)$ be a path with $p\geq 1$ nodes in $H[F,g]$, such that $j_p$ has no out-neighbors in $H[F,g]$.
Node $j_p$ exists since the digraph is acyclic.
Define the maximum capacity reduction as
\[ \sigma^*=\min\left\{\sigma_{j_0j_1}(F,g),\min\left\{g_{j_l,j_{l+1}}-F^*_{j_l,j_{l+1}}: l=1,\ldots,p-1\right\}\right\}>0.\]
Let $\tilde{g}_{j_lj_{l+1}}=g_{j_lj_{l+1}}-\sigma^*$ for $l=0,1,\ldots,p-1$, and let $\tilde{g}_{ij}=g_{ij}$ for all other arcs $(i,j)\in A$.
Then, $(F,\tilde{g},\pi)$ is feasible since, in comparison to $(F,g,\pi)$,  the left hand side of inequality (\ref{con:pf1:flowX}) is
increased by no more than the current slack at node $i=j_0$, reduced at node $i=j_p$, and unchanged at all other nodes $i\in V\setminus D$.
For all arcs $(i,j)$ between non-destination nodes, $\sigma_{ij}(F,\tilde{g})\leq\sigma_{ij}(F,g)$, except from arcs for which $i=j_p$.
But since $(j_p,j)\not\in A[F,g]$, we have that $\sigma_{j_pj}(F,\tilde{g})\leq\tilde{g}_{j_pj}-F^*_{j_pj}=g_{j_pj}-F^*_{j_pj}=0$.
%$\sigma_{j_pj}(F,g)>0$.
% and the capacity reduction introduces no new violations of (\ref{eq:lemlpf2a})--(\ref{eq:lemlpf2c}).
It is finally observed that $\sigma_{j_0j_1}(F,\tilde{g})=0$ if $\sigma^*=\sigma_{j_0j_1}(F,g)$,
and that $\left(j_l,j_{l+1}\right)\in A[F,g]\setminus A[F,\tilde{g}]$ if $\sigma^*=g_{j_l,j_{l+1}}-F^*_{j_l,j_{l+1}}$ for some $l=1,\ldots,p-1$.
\qed\end{proof}

@@

Assume first that $g_{ij}=F_{ij}^*$.
Then, there exists a destination node $t\in D_0\setminus\{i\}$ such that $F_{ij}^t=g_{ij}$.
Because (\ref{eq:lemlpf1a}) gives $F_{ji}^t=0$, flow conservation (\ref{con:pf1:flow}) at node $i$ implies 
$g_{ij}=F_{ij}^t\leq \sum_{k\in V_i\setminus\{j\}}F_{ki}^t\leq \sum_{k\in V_i\setminus\{j\}}g_{ki}$.

@@

The proof that $(X,y,\pi)$ satisfies constraints (\ref{con:dd:arrowFromDest})--(\ref{con:dd:arrowFromNonDestB}), (\ref{con:dd:oneDir})--(\ref{con:dd:startInSource}),
and (\ref{con:dd:yvar}),
follows the proof of Prop.\ \ref{prop:f1strx1}.
To prove (\ref{con:dd:arrowFromNonDestA}), let $i\in V\setminus D$, $j\in V_i$, and $s\in D$.
Then, transformations (\ref{eq:trangX0})--(\ref{eq:trangX}) yield
$X_{ij}^s - \sum_{k\in V_{i}\setminus \{j\}}X_{ki}^s
= g_{ij} - \sum_{k\in V_{i}\setminus \{j\}}g_{ki}$, and (\ref{con:dd:arrowFromNonDestA}) follows from (\ref{eq:lemlpf2d}) in Lemma \ref{lem:lpf2gijgji}.
Because Lemma \ref{lem:lpf2gijgji} also states that $g_{ij}+g_{ji}\leq 1$, we further have that $X_{ij}^s\in[0,1]$ and $y_{ij}\in[0,1]$.
